---
title: "p8105_hw1_lw2883"
author: "Leighanne Wang"
date: "9/13/2020"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```
# Problem 1

#### Creating a data frame with variables

```{r, problem1_df}
problem1_df = tibble(
  norm_sample = rnorm(10),
  norm_sample_pos = norm_sample > 0,
  char_length_10 = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  fact_length_10 = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high")),
)
```
#### Finding the mean of each variable in the data frame

```{r, problem1_df_means, collapse = TRUE, warning = FALSE}
mean(pull(problem1_df, norm_sample))
mean(pull(problem1_df, norm_sample_pos))
mean(pull(problem1_df, char_length_10))
mean(pull(problem1_df, fact_length_10))
```
After trying to take the means of each variable, I find that I am not able to take the mean of characters or factors. I am only able to take the mean of the number and logical variables.

#### Applying *'as.numeric function'* to logical, character, and factor variables

```{r, as.numeric, collapse = TRUE, eval = FALSE}
as.numeric(pull(problem1_df, norm_sample_pos)) 
as.numeric(pull(problem1_df, char_length_10))
as.numeric(pull(problem1_df, fact_length_10))
```
When we apply the 'as.numeric' function, we are unable to apply it to the character vector, it only works for the logical and factor vectors. Factors are converted to the level number through the 'as.numeric' function. Previously, we were unable to take the means of the character and factor vectors because the strings for both vectors contained characters, and it is impossible to take the mean for characters. The logical vector assigns '0' or '1' to 'False' or 'True' respectively and was able to take the mean because of the 0 and 1 assignments.


#### Logical vector conversion 

```{r, logical_vector, collapse = TRUE, warning = FALSE}
as.numeric(pull(problem1_df, norm_sample_pos)) * pull(problem1_df, norm_sample)
as.factor(pull(problem1_df, norm_sample_pos)) * pull(problem1_df, norm_sample)
as.factor(pull(problem1_df, norm_sample_pos))
as.numeric(pull(problem1_df, norm_sample_pos)) * pull(problem1_df, norm_sample)
```

# Problem 2

#### Load the penguins dataset 

```{r, penguins_dataset, results = 'hide'}
data("penguins", package = "palmerpenguins")

summary(penguins)
```

#### Description of Data Set

* This dataset has **8 variables** defined:
  * Species
  * Island
  * Bill length (in mm)
  * Bill depth (in mm)
  * Flipper length (in mm)
  * Body mass (in g)
  * Sex
  * Year
* The information in this dataset is from **`r min(pull(penguins, year))`** to **`r max(pull(penguins, year))`**. It contains information on these 3 different species of penguins: **`r levels(pull(penguins, species))`** from these 3 different islands: **`r levels(pull(penguins, island))`**.
* The dataset has **`r nrow(penguins)`** rows and **`r ncol(penguins)`** columns.
* The mean flipper length is **`r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE))`mm**.

#### Scatterplot

``` {r, scatterplot_penguins, warning = FALSE, message = FALSE}
ggplot(penguins, aes(x = flipper_length_mm, y = bill_length_mm, color = species)) + geom_point()
ggsave("penguins.pdf") 
```