---
title: "p8105_hw1_lw2883"
author: "Leighanne Wang"
date: "9/13/2020"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```
# Problem 1

Creating a data frame with variables

```{r, problem1_df}
problem1_df = tibble(
  norm_sample = rnorm(10),
  norm_sample_pos = norm_sample > 0
)
```
Finding the mean of each variable in data frame

```{r, problem1_df_means, collapse = TRUE}
mean(pull(problem1_df, norm_sample))
mean(pull(problem1_df, norm_sample_pos))
```

Applying as.numeric function to logical, character, and factor variables

```{r, as.numeric, collapse = TRUE}
as.numeric(pull(problem1_df, norm_sample_pos))
```

# Problem 2

Load the penguins dataset 

```{r, penguins_dataset, results = 'hide'}
data("penguins", package = "palmerpenguins")

summary(penguins)
```

Description of Data Set

* This dataset has 8 variables defined including species, island, bill length (in mm), bill depth (in mm), flipper length (in mm), body mass (in g), sex, and year. This dataset has information from **`r min(pull(penguins, year))`** to **`r max(pull(penguins, year))`**. The different species of penguins in this dataset are **`r levels(pull(penguins, species))`** and the different islands in this dataset are **`r levels(pull(penguins, island))`**.
* The dataset has **`r nrow(penguins)`** rows and **`r ncol(penguins)`** columns.
* The mean flipper length is **`r mean(pull(penguins, flipper_length_mm))`**.
